---
title: "Modena"
author: "Mariane Modena"
format: html
---

```{r}
#| message: false
here::i_am("galatic.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Question 1

I already included all the datasets in the first commit...

## Question 2

Link the github repository : [here](https://github.com/MarianeModena/galatic)

## Question 3

```{r}
library(vroom)
planet <- vroom("data/ALL%PLANETS.csv", na=c("missing", NA),locale = locale(grouping_mark = ".", decimal_mark = ",", encoding = "UTF-8"))
```

```{r}
planet |> nrow()
```

There are `r nrow(planet)` planets in the dataset as expected.

```{r}
planet |> ncol()
```

There are `r ncol(planet)` variables in the dataset as expected.

The numerical variables we expect are "mass (earth)", "radius", "density (earth)", "Star_code", "Planet_idx"

```{r}
planet |> select(where(is.numeric))
```

All the expected numerical variables are numeric.

```{r}
planet |> select(where(is.character))
```

## Question 4

```{r}
summary1 <- planet |> summarise(
            "Number of observations" = nrow(planet),
            "Number of variables" = ncol(planet),
            "Number of observations with at least one missing value" = sum(rowSums(is.na(planet)) > 0)
)
                                                              
```





