---
title: "Modena"
author: "Mariane Modena"
format: html
---

```{r}
#| message: false
here::i_am("galatic.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Question 1

I already included all the datasets in the first commit...

## Question 2

Link the github repository : [here](https://github.com/MarianeModena/galatic)

## Question 3

```{r}
library(vroom)
planet <- vroom("data/ALL%PLANETS.csv", na=c("missing", NA),locale = locale(grouping_mark = ".", decimal_mark = ",", encoding = "UTF-8"))
```

```{r}
planet |> nrow()
```

There are `r nrow(planet)` planets in the dataset as expected.

```{r}
planet |> ncol()
```

There are `r ncol(planet)` variables in the dataset as expected.

The numerical variables we expect are "mass (earth)", "radius", "density (earth)", "Star_code", "Planet_idx"

```{r}
planet |> select(where(is.numeric))
```

All the expected numerical variables are numeric.

```{r}
planet |> select(where(is.character))
```

## Question 4

```{r}
summary1 <- planet |> summarise(
            "Number of observations" = nrow(planet),
            "Number of variables" = ncol(planet),
            "Number of observations with at least one missing value" = sum(rowSums(is.na(planet)) > 0)
)
 
knitr::kable(summary1)
```


## Question 5

```{r}
planet |> 
  filter(!is.na(`mass (earth)` & !is.na(`density (earth)`))) |>
  ggplot(aes(x=`mass (earth)`, y=`density (earth)`)) + 
  geom_point()
```

## Question 6 

```{r}
summary2 <- planet |> 
  summarise(
  "densest planet" = which.max(`density (earth)`),
  "least dense planet" = which.min(`density (earth)`),
  "heavier planet" = which.max(`mass (earth)`),
  "lightest planet" = which.min(`mass (earth)`),
  "bigger radius" = which.max(radius),
  "smaller radius" = which.min(radius)
  
            )

knitr::kable(summary2)
```

## Question 7 

```{r}
library(stringr)

terrain <- planet |>
  reframe("terrain" =unlist(str_split(`TYPE_TERRAIN`, ";")))

climat <- planet |>
  reframe("climat" =unlist(str_split(`Climate Type`, ";")))
```



## Question 8 

```{r}
climat |>
  group_by(climat) |>
  summarise("number of climats" = n()) |>
  ggplot(aes(x=`number of climats`)) +
    geom_bar()
```

```{r}

terrain |>
  group_by(terrain) |>
  summarise("number of terrains" = n()) |>
  ggplot(aes(x=`number of terrains`)) + 
  geom_bar()

````

```{r}
terrain |> distinct(terrain)
```

There are 93 different terrains so the distribution looks ok.
